How has the Brazilian Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985

### 2023-02-06 Submission/Re-submission/draft/draft_resubmission.rmd
Added unmeplayoment rate data

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Load data
pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <- ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>%
  select(-location_cat) %>%
  distinct()
ama <- left_join(ama, location_km, by = "location")
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
amazon_def_year_lag <- amazon_def_year
# missing years are missed with first non missing value
adr <- data.frame(year = c(1985, 1986, 1987), 
                  def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 
amazon_def_year_lag$year <- amazon_def_year_lag$year + 1
adr <- data.frame(year = c(1985, 1986, 1987, 1988),
                  def_year = c(21.050, 21.050, 21.050, 21.050))
amazon_def_year_lag <- rbind(adr, amazon_def_year_lag) # Missing year data 
hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
                           "Rousseff", "Temer", "Bolsonaro"))

@@

ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year_lag, by = "year") %>%
dplyr::left_join(AAI, by = "year") %>%
filter(location_cat != "Non Identified") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0),
         mixed_vs_all = ifelse(mx_cat == "Mixed-types", 1, 0))

ama_model2_lag <- dplyr::select(pop, -text) %>%
  dplyr::left_join(amazon_def_year, by = "year") %>%
  dplyr::left_join(AAI, by = "year") %>%
  filter(location_cat != "Non Identified")%>%
  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat),
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries",
                                      location_cat),
                               levels = c("Amazonian States",
                                          "Amazonian Countries",
                                          "International", "Brasilia",
                                          "Non Amazonian States")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0),
        location_cat = factor(case_when(location_cat == "International" ~ 
                                          "Non Amazonian Countries",
                                        location_cat == 
                                          "Amazonian States" ~ 
                                          "Amazonian States",
                                        location_cat == "Amazonian Countries" ~ 
                                          "Amazonian Countries",
                                        TRUE ~ "Non Amazonian States"),
                              levels = c("Amazonian States",
                                         "Amazonian Countries",
                                         "Non Amazonian States",
                                         "Non Amazonian Countries")))
```

@@

c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c5 <- plm(amazon_speech ~ as.factor(location_cat) +
                         def_year + AAI + election_year,
                         data = ama_model2_lag,
                         model = "within", index = "president")

stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = "-12pt",
                      font.size="small",
                      dep.var.labels = c("Amazon Speech",
                                          "Environmental Conservation",
                                         "Economic Integration",
                                         "Social Development",
                                         "National Sovereignty"),
                     covariate.labels = c("Amazonian Countries",
                                          "Non Amazonian States",
                                          "Non Amazonian Countries",
                                          "Deforestation",
                                          "Inflation",
                                          "Election Year",
                                          "High-profile Events"))
```

>>>>

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Load data
pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <- ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>%
  select(-location_cat) %>%
  distinct()
ama <- left_join(ama, location_km, by = "location")
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
amazon_def_year_lag <- amazon_def_year
# missing years are missed with first non missing value
adr <- data.frame(year = c(1985, 1986, 1987), 
                  def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 
amazon_def_year_lag$year <- amazon_def_year_lag$year + 1
adr <- data.frame(year = c(1985, 1986, 1987, 1988),
                  def_year = c(21.050, 21.050, 21.050, 21.050))
amazon_def_year_lag <- rbind(adr, amazon_def_year_lag) # Missing year data 
hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
                           "Rousseff", "Temer", "Bolsonaro"))
urate <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/urate.Rds")

@@

ama_model_lag <- dplyr::left_join(ama_mx,
                                  amazon_def_year_lag, by = "year") %>%
  dplyr::left_join(AAI, by = "year") %>%
  dplyr::left_join(urate, by = "year") %>%
  filter(location_cat != "Non Identified") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation",
                             1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0),
         mixed_vs_all = ifelse(mx_cat == "Mixed-types", 1, 0))

ama_model2_lag <- dplyr::select(pop, -text) %>%
  dplyr::left_join(amazon_def_year, by = "year") %>%
  dplyr::left_join(AAI, by = "year") %>%
  dplyr::left_join(urate, by = "year") %>%
  filter(location_cat != "Non Identified")%>%
  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat),
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries",
                                      location_cat),
                               levels = c("Amazonian States",
                                          "Amazonian Countries",
                                          "International", "Brasilia",
                                          "Non Amazonian States")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0),
        location_cat = factor(case_when(location_cat == "International" ~ 
                                          "Non Amazonian Countries",
                                        location_cat == 
                                          "Amazonian States" ~ 
                                          "Amazonian States",
                                        location_cat == "Amazonian Countries" ~ 
                                          "Amazonian Countries",
                                        TRUE ~ "Non Amazonian States"),
                              levels = c("Amazonian States",
                                         "Amazonian Countries",
                                         "Non Amazonian States",
                                         "Non Amazonian Countries")))
```

@@

c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + UR + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + UR + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + UR + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + UR + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c5 <- plm(amazon_speech ~ as.factor(location_cat) +
                         def_year + AAI + UR + election_year,
                         data = ama_model2_lag,
                         model = "within", index = "president")

stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = "-12pt",
                      font.size="small",
                      dep.var.labels = c("Amazon Speech",
                                          "Environmental Conservation",
                                         "Economic Integration",
                                         "Social Development",
                                         "National Sovereignty"),
                     covariate.labels = c("Amazonian Countries",
                                          "Non Amazonian States",
                                          "Non Amazonian Countries",
                                          "Deforestation",
                                          "Inflation",
                                          "Unemployment rate",
                                          "Election Year",
                                          "High-profile Events"))
```
